### 2021-03-15 paper.Rmd
fix author formatting

---
author:
  - name: Stuart Lee
    affiliation: Monash University
    # use this syntax to add text on several lines
    address: |
      | Department of Econometrics and Business Statistics,
      | Monash University
    email: stuart.a.lee@monash.edu
  - name: Ursula Laa 
    affiliation: University of Natural Resources and Life Sciences
    address:  |
      | Institute of Statistics,
      | University of Natural Resources and Life Sciences
    email:  ursula.laa@boku.ac.at
  - name: Natalia da Silva
    address: |
      | Instituto de Estadística (IESTA), 
      | Universidad de la República
    affiliation: Universidad de la República
    email: natalia@iesta.edu.uy
  - name: Nicholas Spyrison
    address: |
      | Faculty of Information and Technology 
      | Monash University
    affiliation: Monash University
    email: nicholas.spyrison@monash.edu
  - name: Dianne Cook
    address: |
      | Department of Econometrics and Business Statistics,
      | Monash University
    affiliation: Monash University
    email: dicook@monash.edu
  - name: Earo Wang
    address: |
      | Department of Statistics,
      | The University of Auckland
    affiliation: The University of Auckland
    email: earo.wang@auckland.ac.nz
  - name: H. Sherry Zhang
    address: |
      | Department of Econometrics and Business Statistics,
      | Monash University
    affiliation: Monash University
    email: huize.zhang@monash.edu
title:
  formatted: "An Overview of Tours for Dynamic Visualisation of High-dimensional Data"
abstract: > 
  Abstract goes here.
keywords:
  formatted: ["tours", "data visualisation", "high-dimensional data", "data science", "exploratory data analysis"]
output: 
  bookdown::pdf_document2:
    template: template/wires_template_rmd.tex
    keep_tex: true
    toc: false
bibliography: references.bib
biblio-style: apalike
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  fig.show = 'hold',
  dpi = 300 #,
  # out.width = "\\textwidth",
  # fig.path = here::here('img/')
)
```

@@

- subplots trellis literature

- data pipelines (?)

<!-- Original tours (Di)

- What do we mean by multivariate data visualisation?
- multivariate categorical vis, tree maps etc.
-->

@@

# Applications {#application}

@@

>>>>

---
author:
  - name: Stuart Lee
    affiliation: Monash University
    # use this syntax to add text on several lines
    address: |
      | Department of Econometrics and Business Statistics, Monash University
    email: stuart.a.lee@monash.edu
  - name: Ursula Laa 
    affiliation: University of Natural Resources and Life Sciences
    address:  |
      | Institute of Statistics, University of Natural Resources and Life Sciences
    email:  ursula.laa@boku.ac.at
  - name: Natalia da Silva
    address: |
      | Instituto de Estadística (IESTA), Universidad de la República
    affiliation: Universidad de la República
    email: natalia@iesta.edu.uy
  - name: Nicholas Spyrison
    address: |
      | Faculty of Information and Technology, Monash University
    affiliation: Monash University
    email: nicholas.spyrison@monash.edu
  - name: Dianne Cook
    address: |
      | Department of Econometrics and Business Statistics, Monash University
    affiliation: Monash University
    email: dicook@monash.edu
  - name: Earo Wang
    address: |
      | Department of Statistics, The University of Auckland
    affiliation: The University of Auckland
    email: earo.wang@auckland.ac.nz
  - name: H. Sherry Zhang
    address: |
      | Department of Econometrics and Business Statistics, Monash University
    affiliation: Monash University
    email: huize.zhang@monash.edu
title:
  formatted: "An Overview of Tours for Dynamic Visualisation of High-dimensional Data"
abstract: > 
  Abstract goes here.
keywords:
  formatted: ["tours", "data visualisation", "high-dimensional data", "data science", "exploratory data analysis"]
output: 
  bookdown::pdf_document2:
    template: template/wires_template_rmd.tex
    keep_tex: true
    toc: false
bibliography: references.bib
biblio-style: apalike
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  fig.show = 'hold',
  dpi = 300 #,
  # out.width = "\\textwidth",
  # fig.path = here::here('img/')
)
```

@@

<!-- Original tours (Di)
Not sure how much of this wee need to go into...
- subplots trellis literature
- data pipelines (?)
- What do we mean by multivariate data visualisation?
- multivariate categorical vis, tree maps etc.
-->

@@

# Applications {#applications}

@@

* why tours are useful and what we learn from them?
